Bird beak's elaboration and exploration

### 2021-10-19 Analysis/03.1-results.Rmd
Update 03.1-results.Rmd

```{r, eval = TRUE, echo = FALSE, print = FALSE}
library(beer)
```

@@

superorder_shapespace <- MCMCglmm.dispRity(
      data          = shapespace,
      posteriors    = allbirds_8748t_8Dshapespace_31levels,
      group         = MCMCglmm.levels(allbirds_8748t_8Dshapespace_31levels)[c(1:8, 32)],
      rename.groups = c(names(group_names_level_1_2), "phylogeny")[c(1:8, 32)])

order_shapespace <- MCMCglmm.dispRity(
      data          = shapespace,
      posteriors    = allbirds_8748t_8Dshapespace_31levels,
      group         = MCMCglmm.levels(allbirds_8748t_8Dshapespace_31levels)[-c(1:8, 33)],
      rename.groups = c(names(group_names_level_1_2), "phylogeny")[-c(1:8,33)])
```

@@

```{r, eval = TRUE, echo = FALSE, fig.height = 24, fig.width = 24, eval = TRUE}
order_positions_phylo <- get.distributions(results$order_results_phylo, type = "position", exclude.phylo = TRUE)
```
Figure: elaborations distributions per order

```{r, eval = TRUE, echo = FALSE, fig.height = 24, fig.width = 24, eval = TRUE}
order_distances_phylo <- get.distributions(results$order_results_phylo, type = "distance", exclude.phylo = TRUE)
```
Figure: explorations distributions per order

@@

>>>>

```{r, eval = TRUE, echo = FALSE, print = FALSE}
library(dispRity)
```

@@

superorder_shapespace <- MCMCglmm.subsets(
      data          = shapespace,
      posteriors    = allbirds_8748t_8Dshapespace_31levels,
      group         = MCMCglmm.levels(allbirds_8748t_8Dshapespace_31levels)[c(1:8, 32)],
      rename.groups = c(names(group_names_level_1_2), "phylogeny")[c(1:8, 32)])

order_shapespace <- MCMCglmm.subsets(
      data          = shapespace,
      posteriors    = allbirds_8748t_8Dshapespace_31levels,
      group         = MCMCglmm.levels(allbirds_8748t_8Dshapespace_31levels)[-c(1:8, 33)],
      rename.groups = c(names(group_names_level_1_2), "phylogeny")[-c(1:8,33)])
```

@@

```{r, eval = TRUE, echo = FALSE, fig.height = 12, fig.width = 12, eval = TRUE}
order_positions_phylo <- get.distributions(results$order_results_phylo, type = "position", exclude.phylo = TRUE)
```
Figure: elaborations distributions per order

```{r, eval = TRUE, echo = FALSE, fig.height = 12, fig.width = 12, eval = TRUE}
order_distances_phylo <- get.distributions(results$order_results_phylo, type = "distance", exclude.phylo = TRUE)
```
Figure: explorations distributions per order

@@

## Correlations between elaboration and exploration?

```{r, echo = FALSE}
get.correlations <- function(res, cent.tend = median, exclude.phylo = FALSE, ...) {

    ## Remove the phylo one (if needed)
    if(exclude.phylo) {
        select_pos <- names(size.subsets(res$position))
        select_dis <- names(size.subsets(res$distance))
        select_pos <- select_pos[-which(select_pos %in% "phylogeny")]
        select_dis <- select_dis[-which(select_dis %in% "phylogeny")]
        res$position <- get.subsets(res$position, subsets = select_pos)
        res$distance <- get.subsets(res$distance, subsets = select_dis)
    }

    ## Extracting all the results
    disparity_pos <- lapply(res$position$disparity, function(X, type) return(X$elements))
    disparity_dis <- lapply(res$distance$disparity, function(X, type) return(X$elements))

    ## Recentre the results
    disparity_pos <- lapply(disparity_pos, function(X) return(X-0.5))

    ## Measure the central tendencies
    centrals_pos <- lapply(disparity_pos, function(X, fun) apply(X, 1, fun), fun = cent.tend)
    centrals_dis <- lapply(disparity_dis, function(X, fun) apply(X, 1, fun), fun = cent.tend)

    ## Number of groups
    n_groups <- length(centrals_pos)

    ## Calculate and plot the hdrcde
    op_tmp <- par(mfrow = c(ceiling(sqrt(n_groups)), round(sqrt(n_groups))))
    for(i in 1:n_groups) {
        ## Testing the correlation
        cor_test <- cor.test(centrals_pos[[i]], centrals_dis[[i]])
        plot_main <- paste0(names(centrals_pos)[i], ": ", unname(round(cor_test$estimate, 3)), " (p=", unname(round(cor_test$p.value, 3)), ")")
        ## Plotting the results
        plot(centrals_pos[[i]], centrals_dis[[i]], pch = 19, xlab = "elaboration", ylab = "exploration", main = plot_main, cex = 0.5)
    }
    par(op_tmp)
    return(invisible())
}
```

### Correlations per super order (based on phylo)

```{r, eval = TRUE, echo = FALSE, fig.height = 12, fig.width = 12, eval = TRUE}
get.correlations(results$super_results_phylo)
```

### Correlations within super orders

```{r, eval = TRUE, echo = FALSE, fig.height = 12, fig.width = 12, eval = TRUE}
get.correlations(results$super_results_within, exclude.phylo = TRUE)
```

### Correlations per order (based on phylo)

```{r, eval = TRUE, echo = FALSE, fig.height = 12, fig.width = 12, eval = TRUE}
get.correlations(results$order_results_phylo, exclude.phylo = TRUE)
```

### Correlations within orders

```{r, eval = TRUE, echo = FALSE, fig.height = 12, fig.width = 12, eval = TRUE}
get.correlations(results$order_results_within, exclude.phylo = TRUE)
```
